\bf Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2025-07-28 manuscript/manuscript.tex
plots with different bias correction

This approach extends the logic of \citet{babu2004goodness}, who
introduced a similar correction for independent data, to the context
of serially dependent time series via block bootstrapping.
The bias correction term $C_n(x)$ used in the NPB method for
independent data could, in principle, also be approximated by a
bootstrap expectation in the same way as $K_n(x)$.
Nonetheless, under independence, the empirical distribution $F_n(x)$
and the parameter estimate $\hat{\theta}_n$ are already reliable, so
direct calculation of $C_n(x)$ is both simpler and sufficient. The use
of bootstrap expectations as in $K_n(x)$ becomes necessary only when
serial dependence distorts the properties of $F_n(x)$, making
block-bootstrapping-based bias estimation essential.

>>>>

To show that better performance is achieved when using the $K_n(x)$ correction
instead of the $C_n(x)$, we have ad

% This approach extends the logic of \citet{babu2004goodness}, who
% introduced a similar correction for independent data, to the context
% of serially dependent time series via block bootstrapping.
% The bias correction term $C_n(x)$ used in the NPB method for
% independent data could, in principle, also be approximated by a
% bootstrap expectation in the same way as $K_n(x)$.
% Nonetheless, under independence, the empirical distribution $F_n(x)$
% and the parameter estimate $\hat{\theta}_n$ are already reliable, so
% direct calculation of $C_n(x)$ is both simpler and sufficient. The use
% of bootstrap expectations as in $K_n(x)$ becomes necessary only when
% serial dependence distorts the properties of $F_n(x)$, making
% block-bootstrapping-based bias estimation essential.
